On Secure Delegation of SampBQP with a Classical Client

### 2020-03-23 blind.tex
Cite KMThesis
Editorial changes on blindness compiler intro

Here we present our compiler on $\QPIP_0$ protocols that can be used to achieves blindness.
The high level idea is to run the protocol under homomorphic encryption.
Similar idea has happened in
\Ethan{TODO cite thesis} \Ethan{TODO maybe find out more about that ``simulate-able" thing in that thesis and explain the difference in the contexts}.
As we have the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
Compiling it would be a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.

We have a classical client and a quantum server.
We choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
Furthermore, we notice that a ciphertext can be split into registers as with the corresponding plaintext.

A naive approach is to encrypt the initial input,
evaluate the entire protocol homomorphically,
then decode the output at the very end.
However, it is difficult to prove the soundness because... \Ethan{TODO why?}
So instead we let the verifier decrypt every round.
Then, in order the preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
Which results in the following protocol.

@@

\Ethan{Too bottom-up. Need to tell more story.}
We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.

\Ethan{More story here. Talk about stuff like why switch keys.}

@@

>>>>

Here we present our compiler on $\QPIP_0$ protocols that can be used to achieves blindness.
The high level idea is to run the protocol under homomorphic encryption.
A classical version of this compiler appears in \cite{KMThesis}, where it is used to make protocols computationally simulatable.
We have a classical client and a quantum server.
So we choose the quantum homomorphic encryption from \cite{mahadev_qfhe} that's compatible with classical clients.
More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
Furthermore, we notice that the ciphertexts can be split into registers as with the corresponding plaintext.

A naive approach is to encrypt the initial input,
run the entire protocol homomorphically,
then decode the output at the very end.
However, it is difficult to prove the soundness this way because homomorphic encryption schemes doesn't guarantee circuit privacy;
the server could learn about ther client's coins.
Furthermore, the prover would also be allowed to send invalid ciphertexts...?
\Ethan{Can't we assume all ciphertexts are valid, and ``invalid" ones just decodes to $\bot$?}
So instead we let the verifier decrypt every round.
Then, in order the preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
Which results in the following protocol.

@@

@@

This compiler implies a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
To do so, apply it to the protocol from \cite{parallelrep, alagic2019twomessage}.
Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.
